---
title: "Business Data analytics Group 6- Show/No Show classification"
---

### Import data and set objective
```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("knitr")

knitr::opts_knit$set(root.dir = "~/source/big_data/Group6/datasets")
df.train <- read.csv("../datasets/NS.TRAIN.csv")
df.test <- read.csv("../datasets/NS.TEST.csv")
```
Importing the DF

```{r}
dim(df.train)
table(is.na(df.train))
```
##### Dimantion of the DataFrame and missing values

```{r}
summary(df.train)
```
Display the summarize and define a business target

##### Business question
1. Is it possible to predict no show to Dr. appointments?

##### Predictor columnds explained
* patient_id - Patient ID
* appointment - Appointment ID
* week_day - Numeric week day (1-6)
* schedule_date - Schedule date
* appointmnet_date - Appointmnet date
* waiting_time - Diff between Schedule and Appointmnet
* age - Age of patient
* is_female - Sex (boolean)
* scholarship - Scholarshop recieved (boolean)
* neighbourhood - Neighbourhood
* hipertension
* diabetes
* alcoholism
* handcap
* sms_recieved
* poverty - Neighbourhood poverty rank
* x_coor - Langtatude
* y_coor - Latatude
* region - Neighbourhood numeric region 
* no_show - Showed to appointment (boolean)

### EDA and IDA
##### Numeric and Categorical  
numeric     | categorical
----------- | ------------
patient_id  | schedule_date
appointment | appointmnet_date
week_day    | neighbourhood
waiting_time| poverty
age         | -
is_female   | -
scholarship | -

##### which columns have missing values
```{r}
sapply(df.train, function(x) sum(is.na(x)))
```
number of missing values per column

##### which columns to predict
Column to predict is no_show

##### Regression or Classification 
since the Y column is numeric and categorical, the problem is a classification problem

##### Numeric column histograms
```{r}
df = na.omit(df.train)
par(mfrow=c(2,4));
hist(df$week_day, main="week_day", breaks = 10)
hist(log(df$waiting_time+1), main="log waiting_time", breaks = 10)
hist(sqrt(df$age), main="sqrt age", breaks = 10)
hist(df$poverty, main="poverty", breaks = 10)
hist(df$region, main="region", breaks = 10)
hist(log(df$same_day+1), main="log same_day", breaks = 10)
hist(log(df$week_before+1), main="log week_before", breaks = 10)
hist(log(df$ever_before+1), main="log ever_before", breaks = 10)
```

### EDA
#### High probability graphs 
```{r}
# looking for no_show frequencies over waiting time
eda_waiting_time<-aggregate(df.train$no_show, by=list(log(df.train$waiting_time+1)), FUN=mean)
names(eda_waiting_time)=c("waiting time","No show prob")
plot(eda_waiting_time, eda_waiting_time$x, type="p", main="No show prob vs. log waiting time")
```
We can identify a group of confident shows around 100 waiting time (days), or 4.5 in log, whereas the majority is around probability of 0.3

```{r}
eda_week_day<-aggregate(df.train$no_show, by=list(df.train$week_day), FUN=mean)
plot(eda_week_day, eda_week_day$x, type="l", main="No show prob vs. week_day")
```
```{r}
eda_age<-aggregate(df.train$no_show, by=list(sqrt(df.train$age)), FUN=mean)
plot(eda_age, eda_age$x, type="p",  main="No show prob vs. sqrt age")
```

```{r}
eda_scholarship<-aggregate(df.train$no_show, by=list((df.train$scholarship)), FUN=mean)
plot(eda_scholarship, eda_scholarship$x, type="h", col = c("light blue", "blue"), lwd = 100, ylim = c(0.1,0.4), main="No show prob vs. scholarship")
```

```{r}
eda_sms_recieved<-aggregate(df.train$no_show, by=list((df.train$sms_recieved)), FUN=mean)
plot(eda_sms_recieved, eda_sms_recieved$x, type="h", col = c("light blue", "blue"), lwd = 100, ylim = c(0.1,0.4), main="No show prob vs. sms_recieved")
```
#### Low probability graphs
```{r}
par(mfrow=c(2,4))
eda_is_female<-aggregate(df.train$no_show, by=list(df.train$is_female), FUN=mean)
plot(eda_is_female, eda_is_female$x, type="l", main="No show prob vs. is_female", ylim=c(0,1))

eda_poverty<-aggregate(df.train$no_show, by=list((df.train$poverty)), FUN=mean)
plot(eda_poverty, eda_poverty$x, type="l", main="No show prob vs. poverty", ylim=c(0,1))

eda_diabetes<-aggregate(df.train$no_show, by=list((df.train$diabetes)), FUN=mean)
plot(eda_diabetes, eda_diabetes$x, type="l", main="No show prob vs. diabetes", ylim=c(0,1))

eda_hipertension<-aggregate(df.train$no_show, by=list((df.train$hipertension)), FUN=mean)
plot(eda_hipertension, eda_hipertension$x, type="l", main="No show prob vs. hipertension", ylim=c(0,1))

eda_handcap<-aggregate(df.train$no_show, by=list((df.train$handcap)), FUN=mean)
plot(eda_handcap, eda_handcap$x, type="l", main="No show prob vs. handcap", ylim=c(0,1))

eda_same_day<-aggregate(df.train$no_show, by=list((df.train$same_day)), FUN=mean)
plot(eda_same_day, eda_same_day$x, type="l", main="No show prob vs. same_day", ylim=c(0,1))

eda_week_before<-aggregate(df.train$no_show, by=list((df.train$week_before)), FUN=mean)
plot(eda_week_before, eda_week_before$x, type="l", main="No show prob vs. week_before", ylim=c(0,1))

eda_ever_before<-aggregate(df.train$no_show, by=list((df.train$ever_before)), FUN=mean)
plot(eda_ever_before, eda_ever_before$x, type="l", main="No show prob vs. ever_before", ylim=c(0,1))
     
```

### Modeling
#### Logistic Model
```{r}
logit_model <- glm(no_show ~ (age)^4+
                         log(waiting_time+1)+
                         scholarship+
                         sms_recieved+
                         hipertension+
                         diabetes+
                         alcoholism+
                         handcap+
                         poverty+
                         region, data = df.train, family = binomial)
summary (logit_model)
plot(logit_model)
```


#### CART
```{r}
pacman::p_load("tree")
noshow.CART <- tree(no_show ~ week_day+
                      waiting_time+
                      age+
                      is_female+
                      scholarship+
                      hipertension+
                      diabetes+
                      alcoholism+
                      handcap+
                      sms_recieved+
                      poverty+
                      region ,data = df.train)
plot(noshow.CART)
text(noshow.CART, pretty = 0, cex=0.5)
summary(noshow.CART)
```

#### RF
```{r}
pacman::p_load("randomForest")
set.seed(7)
noshow.RF <- randomForest(no_show ~ week_day
                          +waiting_time
                          +age
                          +is_female
                          +scholarship
                          +sms_recieved
                          +poverty
                          +region
                          , data = df.train, na.action=na.omit, type="classification", ntree=100) 
plot(noshow.RF)
#importance(noshow.RF)
varImpPlot(noshow.RF)
```

#### GBM
```{r}
# install.packages("gbm",repos = "http://cran.us.r-project.org")
#library("gbm")
pacman::p_load("gbm")
set.seed(7) #same seed to repeat the RF
no_show.gbm <- gbm (no_show ~ week_day+
                         waiting_time+
                         age+
                         is_female+
                         scholarship+
                         sms_recieved+
                         poverty+
                         region ,data = df.train, n.trees = 1000, interaction.depth = 4, shrinkage = 0.2, verbose = F)
no_show.gbm
summary(no_show.gbm)
```


### Model evaluation
#### Logistic Model
```{r}
threshold = 0.6
fitted.lm.results <- predict(logit_model,df.test,type='response')
lm.prediction <- ifelse(fitted.lm.results > threshold,1,0)
lm.accuracy <- mean(lm.prediction == df.test$no_show)
lm.accuracy
```
```{r}
#install.packages("caret",repos = "http://cran.us.r-project.org") 
#library("caret")
#install.packages("e1071",repos = "http://cran.us.r-project.org")
#library("e1071")
pacman::p_load("caret")
pacman::p_load("e1071")
confusionMatrix(data = lm.prediction, reference =  df.test$no_show)
```

```{r}
cross.table <- table(lm.prediction, df.test$no_show)

l <- nrow(cross.table)
if(l< 2)  {
          cross.table <- rbind(cross.table, c(0,0))
          }

accuracy <- (cross.table[1,1]+cross.table[2,2])/ (cross.table[1,1]+cross.table[2,2]+cross.table[1,2]+cross.table[2,1])
precision <- cross.table[2,2]/(cross.table[2,2]+cross.table[2,1])
recall <- cross.table[2,2]/(cross.table[2,2]+cross.table[1,2])
f1 <- 2*(recall*precision)/(recall+precision)

paste("Accuracy -",accuracy)
paste("Precision -",precision)
paste("Recall -",recall)
paste("F1 -",f1)
```

```{r}
#install.packages("pROC",repos = "http://cran.us.r-project.org")
pacman::p_load("pROC")
plot(roc(df.test$no_show, fitted.lm.results, direction="<"), col="blue", main="Left ROC curve")
```

#### CART
```{r}
<<<<<<< HEAD
threshold = 0.3
=======
<<<<<<< HEAD
threshold = 0.3
=======
threshold = 0.6
>>>>>>> 4b865442aa082d596a80744b97f606f45d5577c7
>>>>>>> 267c5cba95fa80cf8cacbb09a531c7f4ee3af05e
fitted.cart.results <- predict(noshow.CART,df.test)
summary(fitted.cart.results)

cart.prediction <- ifelse(fitted.cart.results > threshold,1,0)
summary(cart.prediction)
```

```{r}
cross.table <- table(cart.prediction, df.test$no_show)

l <- nrow(cross.table)
if(l< 2)  {
          cross.table <- rbind(cross.table, c(0,0))
          }

accuracy <- (cross.table[1,1]+cross.table[2,2])/ (cross.table[1,1]+cross.table[2,2]+cross.table[1,2]+cross.table[2,1])
precision <- cross.table[2,2]/(cross.table[2,2]+cross.table[2,1])
recall <- cross.table[2,2]/(cross.table[2,2]+cross.table[1,2])
f1 <- 2*(recall*precision)/(recall+precision)

paste("Accuracy -",accuracy)
paste("Precision -",precision)
paste("Recall -",recall)
paste("F1 -",f1)
```

#### RF
```{r}
threshold <- 0.5
fitted.rf.results <- predict(noshow.RF,df.test)
summary(fitted.rf.results)
rf.prediction <- ifelse(fitted.rf.results > threshold,1,0)
summary(rf.prediction)
```

```{r}
cross.table <- table(rf.prediction, df.test$no_show)

l <- nrow(cross.table)
if(l< 2)  {
          cross.table <- rbind(cross.table, c(0,0))
          }

accuracy <- (cross.table[1,1]+cross.table[2,2])/ (cross.table[1,1]+cross.table[2,2]+cross.table[1,2]+cross.table[2,1])
precision <- cross.table[2,2]/(cross.table[2,2]+cross.table[2,1])
recall <- cross.table[2,2]/(cross.table[2,2]+cross.table[1,2])
f1 <- 2*(recall*precision)/(recall+precision)

paste("Accuracy -",accuracy)
paste("Precision -",precision)
paste("Recall -",recall)
paste("F1 -",f1)
```

#### GBM
```{r}
threshold <- 0.6
fitted.gbm.results <- predict(no_show.gbm,df.test, n.trees = 1000)
summary(fitted.gbm.results)
gbm.prediction <- ifelse(fitted.gbm.results > threshold,1,0)
summary(gbm.prediction)
```

```{r}
cross.table <- table(gbm.prediction, df.test$no_show)

l <- nrow(cross.table)
if(l< 2)  {
          cross.table <- rbind(cross.table, c(0,0))
          }
accuracy <- (cross.table[1,1]+cross.table[2,2])/ (cross.table[1,1]+cross.table[2,2]+cross.table[1,2]+cross.table[2,1])
precision <- cross.table[2,2]/(cross.table[2,2]+cross.table[2,1])
recall <- cross.table[2,2]/(cross.table[2,2]+cross.table[1,2])
f1 <- 2*(recall*precision)/(recall+precision)

paste("Accuracy -",accuracy)
paste("Precision -",precision)
paste("Recall -",recall)
paste("F1 -",f1)
```

