---
title: "Business Data analytics Group 6- Show/No Show classification"
output: NS_classi
---

### Import data and set objective
```{r}
#library(knitr)
knitr::opts_knit$set(root.dir = "~/source/big_data/Group6/datasets")
df.train <- read.csv("../datasets/NS.TRAIN.csv")
df.test <- read.csv("../datasets/NS.TEST.csv")
```
Importing the DF

```{r}
dim(df.train)
table(is.na(df.train))
```
##### Dimantion of the DataFrame and missing values

```{r}
summary(df.train)
```
Display the summarize and define a business target

##### Business question
TBD
##### Predictor columnds explained
* patient_id - 
* appointment - 
* week_day - 
* schedule_date - 
* appointmnet_date -
* waiting_time - 
* age - 
* is_female - 
* scholarship - 
* neighbourhood
* hipertension
* diabetes
* alcoholism
* handcap
* sms_recieved
* no_show
* poverty
* x_coor
* y_coor
* region

##### Evaluation matric of models
 
TBD

### EDA and IDA
##### Numeric and Categorical  
numeric| categorical
------ | --------
X      | country
Price  | designation
points | province
  -    | region_1+2
  -    | variety
  -    | description
  -    | country
  -    | winery

##### which columns have missing values
```{r}
sapply(df.train, function(x) sum(is.na(x)))
```
number of missing values per column

##### which columns to predict
Column to predict is no_show

##### Regression or Classification 
since the Y column is numeric and categorical, the problem is a classification problem

##### Numeric column histograms
```{r}
df = na.omit(df.train)
par(mfrow=c(2,3));
hist(df$week_day, main="week_day", breaks = 10)
hist(df$waiting_time, main="waiting_time", breaks = 10)
hist(df$age, main="age", breaks = 10)
hist(df$poverty, main="poverty", breaks = 10)
hist(df$region, main="region", breaks = 10)
```

### Modeling
#### LM
```{r}
logit_all_model <- glm(no_show ~ week_day+
                         waiting_time+
                         age+
                         is_female+
                         scholarship+
                         hipertension+
                         diabetes+
                         alcoholism+
                         handcap+
                         sms_recieved+
                         poverty+
                         region
                       , data = df.train, family = binomial)
summary (logit_all_model)
plot(logit_all_model)
```

#### CART
```{r}
library("tree")
noshow.CART <- tree(no_show ~ week_day+
                         waiting_time+
                         sqrt(age)+
                         is_female+
                         scholarship+
                         hipertension+
                         diabetes+
                         alcoholism+
                         handcap+
                         sms_recieved+
                         poverty+
                         region ,data = df.train)
plot(noshow.CART)
text(noshow.CART, pretty = 0, cex=0.5)
summary(noshow.CART)

```

#### RF
```{r}
library("randomForest")
set.seed(7)
noshow.RF <- randomForest(no_show ~ week_day+
                         waiting_time+
                         age+
                         is_female+
                         scholarship+
                         sms_recieved+
                         poverty+
                         region, data = df.train, na.action=na.omit) 
plot(noshow.RF)
noshow.RF
importance(noshow.RF)
varImpPlot(noshow.RF)
```

#### GBM
```{r}
#install.packages("gbm",repos = "http://cran.us.r-project.org")
library("gbm")
set.seed(7) #GBM includes random selection. Repeat same seed to repeat the RF
no_show.gbm <- gbm (no_show ~ week_day+
                         waiting_time+
                         age+
                         is_female+
                         scholarship+
                         sms_recieved+
                         poverty+
                         region,data = df.train, n.trees = 1000, interaction.depth = 4, shrinkage = 0.2, verbose = F) #gbm distribution is gaussian for regression and bernoulli for binary classification
no_show.gbm
summary(no_show.gbm)
```


### Model evaluation
```{r}
# Global threshold decleration
threshold = 0.5
```

#### LM
```{r}
lm_y_est <- predict(lm.model2, df.test)
lm_res <- lm_y_est - df.test$price_log
hist(lm_res)
L1 = sum(abs(lm_res))/length(lm_res)
Res_sq <- lm_res^2
RSS <- sum(Res_sq)
MSE <- RSS/length(Res_sq)
RMSE <- sqrt(MSE)
RMSE
```

#### CART
```{r}
CART.results = predict(Wine.CART, df.test, n.trees = 1000)
summary(CART.results)
CART.prediction = ifelse(CART.results > threshold)
summary(CART.prediction)

Residual <- CART.results - df.test$price_log
Res_sq <- Residual * Residual
RSS <- sum(Res_sq)
MSE <- mean(Res_sq)
RMSE <- sqrt(MSE)
Total_res <- CART.results - mean(df.test$price_log)
TSS <- sum(Total_res*Total_res)
R2 <- 1- RSS/TSS
R2
```

#### RF
```{r}
RF.results = predict(Wine.RF, df.test)
summary(RF.results)
RF.prediction = ifelse(RF.results > threshold,1,0)
summary(RF.prediction)

# CROSS TABLE INSERTION
```

#### GBM
```{r}
GBM.results = predict(Wine.gbm, df.test, n.trees = 1000)
summary(GBM.results)
GBM.prediction = ifelse(GBM.results > threshold,1,0)
summary(GBM.prediction)
```

