---
title: "Wine"
author: "Rotem Zaarour & Dor Heldshtein & Lior Rosen"
date: "January 2018"
output:
  html_notebook: default
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

### 1. The data - EDA and preparing the DATA

**Reading, and understanding the DATA: **

>Data source:
   https://www.kaggle.com/zynicide/wine-reviews/data

```{r}
df <- read.csv('C:/Users/My-PC/Desktop/studies/Sem02/Data_Analytics_for_Business2-G.Shama/Wine_Protject/Data/winemag-data-130k-v2.csv') # Change this path to your downloaded file
```

Exemaining n/a:
```{r Exemaining n/a:}
# checking for missing data and cleaning the n/a
print(colSums(is.na(df)))
# as we see we have some n/a in the price so we sould clean it:
df <- df[!is.na(df$price), ]
df <- df[(df$country!= ""), ]
#df <- df[(df$price != ""), ]
```

Quick glance at the data:
```{r Quick glance at the data:}
str(df)
a.df = c("country","province", "region_1", "region_2", "points", "price", "designation", "variety", "winery", "taster_name")
summary(df[,a.df])
```

Summary of unique velues:
```{r}
unique_vals <- sapply(df, unique)
summary(unique_vals)
```

**Enriching the DATA**

adding the wine types by red and white
```{r}
# the following chunk requires installation of the package dplyr
library(dplyr)

df$wine_type = ifelse(df$variety == "Chardonnay" | df$variety == "Riesling" | df$variety == "Sauvignon Blanc" | df$variety == "White Blend" | df$variety == "Sparkling Blend" | df$variety == "Pinot Gris" | df$variety == "Champagne Blend" | df$variety == "Grüner Veltliner" | df$variety == "Pinot Grigio" | df$variety == "Portuguese White" | df$variety == "Viognier" | df$variety == "Gewürztraminer" | df$variety == "Gewürztraminer", 
                              "White Wine",
                              "Red Wine")
df$wine_type = as.factor(df$wine_type)  
summary(df$wine_type)
```

adding each country the mean of her score points and price:
```{r}
mean_pricePcntry = aggregate(price~country, data=df, mean)
mean_pointsPcntry = aggregate(points~country, data=df, mean)

enrich_means = merge(mean_pointsPcntry, mean_pricePcntry, by = "country")
colnames(enrich_means) = c("country", "m.pntPcntry", "m.prcPcntry")
df = merge(df, enrich_means, by = "country")

```

adding external data ??

**Lets inspect the DATA: **

First we would like to analys the distribution:

* the points of critic.
* the price (only under 150 to reduce the edges).
* the price's log.

```{r}
# the following chunk requires the installation of the package ggplot

library(ggplot2)
library(ggjoy)
library(gridExtra)
library(ggridges)

ggplot(data = df, aes(x= points, colour = I('black'), fill = I('#099DD9')))+geom_histogram(binwidth = 1)+labs(x = "Points", y= "Frequency", title = "Wine Review - Points histogram")
summary(df$points)

ggplot(data = df[(df$price<150),], aes(x= price, colour = I('black'), fill = I('#099DD9')))+geom_histogram()+labs(x = "Price", y= "Frequency", title = "Wine Reviews - Price Histrogram")
summary(df$price)
ggplot(data = df, aes(x= log(price), colour = I('black'), fill = I('#099DD9')))+geom_histogram()+labs(x = "log(Price)", y= "Frequency", title = "Wine Reviews - Log(prices) Histogram")
summary(log(df$price))

desc = data.frame(nw = (lengths(gregexpr(" ", df$description))+1))
ggplot(data = desc, aes(x= nw, colour = I('black'), fill = I('#099DD9')))+geom_histogram()+labs(x = "Words", y= "Frequency", title = "Wine Reviews - Description words amount Histogram")
summary(desc$nw)
```

Now we would see the difrences between:

* Top 20 wine types.
* Red and White wines.

Top 20 types of wine
```{r}
top_20_wines <- df %>%
  group_by(variety) %>%
  summarise(count = n())%>%
  arrange(desc(count))

top_20_wines <- top_20_wines[1:20,1:2]

top_20_wines
top_20_wines <- top_20_wines$variety  
top_20.df <- subset(df, variety %in% top_20_wines)
```

```{r}
top_20.df[(top_20.df$price <= 100 & top_20.df$price >0),] %>%
  group_by(variety, wine_type) %>%
  summarise(n=n(),
            avg_score = mean(points),
            avg_price = mean(price)) %>%
  ggplot(aes(x=avg_price, y= avg_score, size = n, colour = wine_type))+
  geom_point()+
  scale_color_manual(values = c("#990000", "#FFFF66"))

```



```{r}
p1 <- ggplot(data = subset(top_20.df, wine_type == "Red Wine"), aes(x=points, y=variety))+
  geom_density_ridges2(bandwidth = 0.539, fill = "#990000")

p2 <- ggplot(data = subset(top_20.df, wine_type == "White Wine"), aes(x=points, y=variety))+
  geom_density_ridges2(bandwidth = 0.539, fill = "#FFFF66")

grid.arrange(p1, p2, nrow = 1)
```

```{r}
p3 <- ggplot(data = subset(top_20.df, wine_type == "Red Wine"), aes(x=log(price), y=variety))+
  geom_joy2(bandwidth = 0.103, fill = "#990000")

p4 <- ggplot(data = subset(top_20.df, wine_type == "White Wine"), aes(x=log(price), y=variety))+
  geom_joy2(bandwidth = 0.103, fill = "#FFFF66")

grid.arrange(p3, p4, nrow=1)
```

```{r}
# the following requires installation of gridExtra package
p5 <- ggplot(data = subset(top_20.df, wine_type == "Red Wine"), aes(x=points, y= price))+
  geom_point(colour="#990000")+
  scale_y_log10()+
  geom_smooth()

p6 <- ggplot(data = subset(top_20.df, wine_type == "White Wine"), aes(x=points, y= price))+
  geom_point(colour="#FFFF66")+
  scale_y_log10()+
  geom_smooth()


cor(log(top_20.df$price), top_20.df$points)

grid.arrange(p5, p6, nrow=1)
```

### 2. Analysing the data - predicting regression

**filter and split to train and test, as learned before:**

```{r}
set.seed(7) # Split to train 80% and test 20%
bound <- floor((nrow(df)/5)*4)
d <- df[sample(nrow(df)), ]
df.train <- d[1:bound, ]
df.test <- d[(bound+1):nrow(df), ]
```

**prepearing the DATA:**

```{r prepering the train DATA:}
clean_train = data.frame(points = df.train$points,
                     price = log(df.train$price),
                     desc_nc = nchar(as.character(df.train$description)),
                     desc_nw = (lengths(gregexpr(" ", df.train$description))+1),
                     DnwPpoint = log(lengths(gregexpr(" ", df.train$description))*1)+df.train$points,
                     title_nc = nchar(as.character(df.train$title)),
                     cntry_code = as.numeric(df.train$country),
                     lg.price_points = log(df.train$price)*df.train$points,
                     cntry_pnts = as.numeric(df.train$country)*df.train$points,
                     pntPcntry = df.train$m.pntPcntry,
                     prcPcntry = df.train$m.prcPcntry,
                     cntry_m.points = as.numeric(df.train$country)*df.train$m.prcPcntry,
                     isred = ifelse(df.train$wine_type == "White Wine", 0, 1)
                     )
summary(clean_train)
```

###Cheking the coralation:

```{r}
cor(clean_train, clean_train)
```


~ we can see that we have coralation between ?? ~

```{r}
pairs(clean_train[c(2,1,3,4)], col = "blue", cex = 0.5, upper.panel = NULL)
```

**checking the test:**

```{r prepering the test DATA:}
clean_test = data.frame(points = df.test$points,
                     price = log(df.test$price),
                     desc_nc = nchar(as.character(df.test$description)),
                     desc_nw = (lengths(gregexpr(" ", df.test$description))+1),
                     DnwPpoint = log(lengths(gregexpr(" ", df.test$description))*1)+df.test$points,
                     title_nc = nchar(as.character(df.test$title)),
                     cntry_code = as.numeric(df.test$country),
                     lg.price_points = log(df.test$price)*df.test$points,
                     cntry_pnts = as.numeric(df.test$country)*df.test$points,
                     pntPcntry = df.test$m.pntPcntry,
                     prcPcntry = df.test$m.prcPcntry,
                     cntry_m.points = as.numeric(df.test$country)*df.test$m.prcPcntry,
                     isred = ifelse(df.test$wine_type == "White Wine", 0, 1)
                     )
summary(clean_train)
```

###Cheking the coralation:

```{r}
cor(clean_test, clean_test)
```


~ we can see that we have coralation between ?? ~

```{r}
pairs(clean_test[c(2,1,3,4)], col = "blue", cex = 0.5, upper.panel = NULL)
```


```{r}
# Regression Models
# Linear Regression

Price_points_reg1 <- lm(log(price) ~ points, data = clean_train)
summary(Price_points_reg1)

par(mfrow = c(2,2))
plot(Price_points_reg1)

Price_points_reg2 <- lm(log(price) ~ points + isred, data = clean_train)
summary(Price_points_reg2)

par(mfrow = c(2,2))
plot(Price_points_reg2)


Price_points_reg3 <- lm(log(price) ~ points^2 + points + isred, data = clean_train)
summary(Price_points_reg3)

par(mfrow = c(2,2))
plot(Price_points_reg3)
```

```{r}
# Applying the Regression Model on the Test Data

#Price_points_reg1_test <- lm(log(price) ~ points, data = clean_test)
#summary(Price_points_reg1_test)

#par(mfrow = c(2,2))
#plot(Price_points_reg1)

Price_points_reg2_test <- lm(log(price) ~ points + points*desc_nc + isred, data = clean_test)
summary(Price_points_reg2_test)

par(mfrow = c(2,2))
plot(Price_points_reg2)


#Price_points_reg3_test <- lm(log(price) ~ points^2 + points + isred, data = clean_test)
#summary(Price_points_reg3_test)

#par(mfrow = c(2,2))
#plot(Price_points_reg3)


```

### Tree (CART)
#### Model learning on Train data
# Running the tree model for all predictors, and then viewing the model summary and plot:
```{r}

#install.packages("tree")
library("tree")
tree_train = data.frame(price = log(df.train$price), ##Price :)
                        Verity = as.numeric(ifelse(df.train$wine_type == "Red Wine",
                                        2,
                                        1)),
                        pnt_desc = df.train$points*as.integer(df.train$description), ##number of chars in the description
                        region = df.train$region_2,
                        Pointsabv90 = ifelse(df.train$points >= 90,
                                        T,
                                        F) ##logical yes = above 90
)

tree_model = tree(price ~., tree_train)
plot(tree_model)
text(tree_model, pretty = 1, cex = 0.5)

summary(tree_model)
#train = points - ## logical yes above 90
#new.df.train <- df.train[c(-1,-3,-12)] # trying to clean from irrelevant variables for the #CART Tree Model
#Wine_Tree <- tree(new.df.train$points ~ . , data = new.df.train) #Train this tree with all #predictors
#
#plot(Wine_Tree)
#text(Wine_Tree, pretty = 0, cex=0.5)

# Ranfom Forest 
#
#
# GBM 
#
#
#

```
```{r}
summary (Wine_Tree)

```
```{r}
Wine_Tree

```


#### Model evaluation on Test data

First predict the "left" value for the test data. Prediction is a probability between 0 to 1. 
```{r}
fitted.results <- predict(Wine_Tree,df.test)
summary(fitted.results)

```


```{r}
# Textual analysis of the wine reviews

# Analyzing how many words are there in each review
new_data$wordcount <- sapply(gregexpr("\\S+", new_data$description), length)

summary(new_data$wordcount)

ggplot(data = new_data, aes(x= wordcount))+
  geom_histogram(binwidth = 3)+
  labs(x = "Number of Words", y= "Frequency", title = "Nomber of words in Wine reviews") 

ggplot(data = new_data, aes(x= wordcount, y= wine_type, fill = wine_type))+
  geom_density_ridges ()+
  labs(x = "Word Count", title = "Distribution of word count of description")+
  scale_fill_cyclical(values = c("#CC3300", "#FFCC00"))

ggplot(data = new_data, aes(x=variety, y=wordcount))+
  geom_boxplot()+
  coord_flip()+
  labs(title = "Wordcount Distribution by Variety", x= "Variety", y= "Word Count")
```

```{r}
# ggplot(data = new_data, aes(x=wordcount, y=points))+geom_point()

Price_points_reg4 <- lm(log(price) ~ points + new_data$wordcount , data = new_data)
summary(Price_points_reg4)

par(mfrow = c(2,2))
plot(Price_points_reg4)
```
```{r}
# Applying Regression on Test Data

Price_points_reg5 <- lm(log(price) ~ points + new_data$wordcount , data = df.test)
summary(Price_points_reg5)

par(mfrow = c(2,2))
plot(Price_points_reg5)

  ```
