---
title: "Wine"
author: "Rotem Zaarour & Dor Heldshtein & Lior Rosen"
date: "January 2018"
output:
  html_notebook: default
  word_document: default
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Reading The data, EDA and data preparation

**Reading, and understanding the DATA: **

>Data source:
   https://www.kaggle.com/zynicide/wine-reviews/data

```{r}
df <- read.csv('C:/Users/Meni/Downloads/winemag-data-130k-v2.csv') # Change this path to your downloaded file
```

Exemaining n/a:
```{r Exemaining n/a:}
# checking for missing data and cleaning the n/a
print(colSums(df == "")
# as we see we have some n/a in the price so we sould clean it:
df <- df[!is.na(df$price), ]
#we would also like to clean the blanks country rows:
df <- df[(df$country!= ""), ]
```

Quick glance at the data:
```{r Quick glance at the data:}
str(df)
a.df = c("country","province", "region_1", "region_2", "points", "price", "designation", "variety", "winery", "taster_name")
summary(df[,a.df])
```

Summary of unique values:
```{r}
unique_vals <- sapply(df, unique)
summary(unique_vals)
```

**Exploring the DATA**

Defining wine types by red and white
```{r}
# the following chunk requires installation of the package dplyr
library(dplyr)

df$wine_type = ifelse(df$variety == "Chardonnay" | df$variety == "Riesling" | df$variety == "Sauvignon Blanc" | df$variety == "White Blend" | df$variety == "Sparkling Blend" | df$variety == "Pinot Gris" | df$variety == "Champagne Blend" | df$variety == "Grüner Veltliner" | df$variety == "Pinot Grigio" | df$variety == "Portuguese White" | df$variety == "Viognier" | df$variety == "Gewürztraminer" | df$variety == "Gewürztraminer", 
                              "White Wine",
                              "Red Wine")
df$wine_type = as.factor(df$wine_type)  
summary(df$wine_type)
```

adding the ratio between price and points:
```{r}
df$ratio = ((log(df$price))/df$points)*100
summary(df$ratio)
```

adding external data ??

**Lets inspect the DATA: **

First we would like to analyze the distribution:

* the points (score) given in each wine criticism.
* the price (only under 150 to reduce the edges).
* the price's log.

```{r}
# the following chunk requires the installation of the package ggplot

library(ggplot2)
library(ggjoy)
library(gridExtra)
library(ggridges)

ggplot(data = df, aes(x= points, colour = I('black'), fill = I('#099DD9')))+geom_histogram(binwidth = 1)+labs(x = "Points", y= "Frequency", title = "Wine Review - Points histogram")
summary(df$points)

ggplot(data = df[(df$price<150),], aes(x= price, colour = I('black'), fill = I('#099DD9')))+geom_histogram()+labs(x = "Price", y= "Frequency", title = "Wine Reviews - Price Histrogram")
summary(df$price)
ggplot(data = df, aes(x= log(price), colour = I('black'), fill = I('#099DD9')))+geom_histogram()+labs(x = "log(Price)", y= "Frequency", title = "Wine Reviews - Log(prices) Histogram")
summary(log(df$price))

desc = data.frame(nw = (lengths(gregexpr(" ", df$description))+1))
ggplot(data = desc, aes(x= nw, colour = I('black'), fill = I('#099DD9')))+geom_histogram()+labs(x = "Words", y= "Frequency", title = "Wine Reviews - Description words amount Histogram")
summary(desc$nw)
```

Now we would like to take a closer look at the differences between white and red wines, among the top 20 wine varieties in the data:

Top 20 types of wine
```{r}
top_20_wines <- df %>%
  group_by(variety) %>%
  summarise(count = n())%>%
  arrange(desc(count))

top_20_wines <- top_20_wines[1:20,1:2]

top_20_wines
top_20_wines <- top_20_wines$variety  
top_20.df <- subset(df, variety %in% top_20_wines)
```

Now let's explore how price and rating are distributed within white and red wines
```{r}
top_20.df[(top_20.df$price <= 100 & top_20.df$price >0),] %>%
  group_by(variety, wine_type) %>%
  summarise(n=n(),
            avg_score = mean(points),
            avg_price = mean(price)) %>%
  ggplot(aes(x=avg_price, y= avg_score, size = n, colour = wine_type))+
  geom_point()+
  scale_color_manual(values = c("#990000", "#FFFF66"))

```


Let's take a deeper look into specific wine varieties among the white and red groups, and see what we can learn from analyzing their price and rating (points)
```{r}
p1 <- ggplot(data = subset(top_20.df, wine_type == "Red Wine"), aes(x=points, y=variety))+
  geom_density_ridges2(bandwidth = 0.539, fill = "#990000")

p2 <- ggplot(data = subset(top_20.df, wine_type == "White Wine"), aes(x=points, y=variety))+
  geom_density_ridges2(bandwidth = 0.539, fill = "#FFFF66")

grid.arrange(p1, p2, nrow = 1)
```
We will look at the log of price, in view of its broad distribution, as we saw earlier in the histogram
```{r}
p3 <- ggplot(data = subset(top_20.df, wine_type == "Red Wine"), aes(x=log(price), y=variety))+
  geom_joy2(bandwidth = 0.103, fill = "#990000")

p4 <- ggplot(data = subset(top_20.df, wine_type == "White Wine"), aes(x=log(price), y=variety))+
  geom_joy2(bandwidth = 0.103, fill = "#FFFF66")

grid.arrange(p3, p4, nrow=1)
```
Exploring the relation between price and points for white and red wines
```{r}
# the following requires installation of gridExtra package
p5 <- ggplot(data = subset(top_20.df, wine_type == "Red Wine"), aes(x=points, y= price))+
  geom_point(colour="#990000")+
  scale_y_log10()+
  geom_smooth()

p6 <- ggplot(data = subset(top_20.df, wine_type == "White Wine"), aes(x=points, y= price))+
  geom_point(colour="#FFFF66")+
  scale_y_log10()+
  geom_smooth()


cor(log(top_20.df$price), top_20.df$points)

grid.arrange(p5, p6, nrow=1)
```

### 2. Analyzing the data - exploring regressions

**filter and split to train and test, as learned before:**

```{r}
set.seed(7) # Split to train 80% and test 20%
bound <- floor((nrow(df)/5)*4)
d <- df[sample(nrow(df)), ]
df.train <- d[1:bound, ]
df.test <- d[(bound+1):nrow(df), ]
```

**prepearing the DATA:**
### building data frame:
building train data frame:
```{r prepering the train DATA:}
clean_train = data.frame(points = df.train$points,
                         price = df.train$price,
                         ratio = df.train$ratio,
                         desc_nw = (lengths(gregexpr(" ", df.train$description))+1),
                         DnwPpoint = log(lengths(gregexpr(" ", df.train$description))*1)+df.train$points,
                         title_nc = nchar(as.character(df.train$title)),
                         cntry_code = as.numeric(df.train$country),
                         isred = ifelse(df.train$wine_type == "White Wine", 0, 1)
                         )
summary(clean_train)
```

lets do the same for the test:
```{r prepering the test DATA:}
clean_test = data.frame(points = df.test$points,
                         price = df.test$price,
                         ratio = df.test$ratio,
                         desc_nw = (lengths(gregexpr(" ", df.test$description))+1),
                         DnwPpoint = log(lengths(gregexpr(" ", df.test$description))*1)+df.test$points,
                         title_nc = nchar(as.character(df.test$title)),
                         cntry_code = as.numeric(df.test$country),
                         isred = ifelse(df.test$wine_type == "White Wine", 0, 1)
                         )
summary(clean_test)
```
### Cheking for correlations:
```{r}
cor(clean_train[clean_train$isred == 0,], clean_train[clean_train$isred == 0,])
```

now let's take a closer look at pairs - for the three main factors (price, points, description length)
```{r}
pairs(clean_train[c(1-4)], col = "blue", cex = 0.5, upper.panel = NULL)
```

Cheking the correlations of the test data:
```{r}
cor(clean_test, clean_test)
```

and also the test data pairs as we did for the train data

```{r}
pairs(clean_test[c(1-4)], col = "blue", cex = 0.5, upper.panel = NULL)
```

**checking the test data:**

Now let's explore possible regression models for predicting the price of a wine
```{r}
# Regression Models
# Linear Regression

Price_points_reg1 <- lm(log(price) ~ points, data = df.train)
summary(Price_points_reg1)

par(mfrow = c(2,2))
plot(Price_points_reg1)

Price_points_reg2 <- lm(log(price) ~ points + wine_type, data = df.train)
summary(Price_points_reg2)

par(mfrow = c(2,2))
plot(Price_points_reg2)


Price_points_reg3 <- lm(log(price) ~ points^2 + points + wine_type, data = df.train)
summary(Price_points_reg3)

par(mfrow = c(2,2))
plot(Price_points_reg3)

Price_points_reg4 <- lm(log(price) ~ points + desc_nw, data = clean_train)
summary(Price_points_reg4)

par(mfrow = c(2,2))
plot(Price_points_reg4)
```

Now let's explore additional regression models for predicting the ratio between wine's rating and price
```{r}
# Regression Models
# Linear Regression

lior_df = clean_train
#lior_df$ratio = log(lior_df$price) / (lior_df$points + 1) 
lior_df$ratio = (lior_df$points + 1) / log(lior_df$price) 

Price_points_reg5 <- lm(ratio ~ desc_nw, data = lior_df)
summary(Price_points_reg5)

par(mfrow = c(2,2))
plot(Price_points_reg5)

Price_points_reg6 <- lm(ratio ~ cntry_code + desc_nw, data = lior_df)
summary(Price_points_reg6)

par(mfrow = c(2,2))
plot(Price_points_reg6)
```


Now let's check the validity of the regression models on the test data as well
```{r}
# Applying the Regression Model on the Test Data

# Regression Models - Linear Regression

Price_points_reg1_test <- lm(log(price) ~ points, data = df.test)
summary(Price_points_reg1_test)

par(mfrow = c(2,2))
plot(Price_points_reg1_test)

Price_points_reg2_test <- lm(log(price) ~ points + wine_type, data = df.test)
summary(Price_points_reg2_test)

par(mfrow = c(2,2))
plot(Price_points_reg2_test)


Price_points_reg3_test <- lm(log(price) ~ points^2 + points + wine_type, data = df.test)
summary(Price_points_reg3_test)

par(mfrow = c(2,2))
plot(Price_points_reg3_test)

Price_points_reg4_test <- lm(log(price) ~ points + desc_nw, data = clean_test)
summary(Price_points_reg4_test)

par(mfrow = c(2,2))
plot(Price_points_reg4_test)

lior_df_test = clean_test
lior_df_test$ratio = log(lior_df_test$price) / (lior_df_test$points + 1) 

Price_points_reg5_test <- lm(ratio ~ desc_nw, data = lior_df_test)
summary(Price_points_reg5_test)

par(mfrow = c(2,2))
plot(Price_points_reg5_test)

Price_points_reg6_test <- lm(ratio ~ desc_nw^2 + desc_nw, data = lior_df_test)
summary(Price_points_reg6_test)

par(mfrow = c(2,2))
plot(Price_points_reg6_test)
```

### 3. Analyzing the Wine Reviews Text

Textual Mining of the wine reviews
```{r}
# Textual analysis of the wine reviews

# Analyzing how many words are there in each review
df.train$wordcount <- sapply(gregexpr("\\S+", df.train$description), length)

summary(df.train$wordcount)

library("ggplot2")
library("ngram")
library("ggridges")
ggplot(data = df.train, aes(x= wordcount))+geom_histogram(binwidth = 3)+labs(x = "Number of Words", y= "Frequency", title = "Nomber of words in Wine reviews") 

ggplot(data = df.train, aes(x= wordcount, y= wine_type, fill = wine_type))+
  geom_density_ridges()+ labs(x = "Word Count", title = "Distribution of word count of description")+
  scale_fill_cyclical(values = c("#CC3300", "#FFCC00"))

ggplot(data = df.train, aes(x=variety, y=wordcount))+
  geom_boxplot()+
  coord_flip()+
  labs(title = "Wordcount Distribution by Variety", x= "Variety", y= "Word Count")
```

Let's take as an example the Red Blend Wines - and perform Text Mining on their reviews
  
```{r}
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")


#---------- Red Wines Word cloud ----------#


#pinot <- subset(df.test, wine_type == "Red Wine")
pinot <- subset(df.test, variety == "Red Blend")

descriptors <- Corpus(VectorSource(pinot$description))
head(descriptors)

# Convert the text to lower case
descriptors <- tm_map(descriptors, content_transformer(tolower))
# Remove numbers
descriptors <- tm_map(descriptors, removeNumbers)
# Remove english common stopwords
descriptors <- tm_map(descriptors, removeWords, stopwords("english"))
# Remove your own stop word
# specify your stopwords as a character vector
descriptors <- tm_map(descriptors, removeWords, c("wine", "pinot", "noir", "drink", "flavors")) 
# Remove punctuations
descriptors <- tm_map(descriptors, removePunctuation)
# Eliminate extra white spaces
descriptors <- tm_map(descriptors, stripWhitespace)
# Text stemming
#descriptors <- tm_map(descriptors, stemDocument)

# Build a term-document matrix
dtm <- TermDocumentMatrix(descriptors)
dtm_mat <- as.matrix(dtm)
v <- sort(rowSums(dtm_mat),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 20)
# Generate the Word cloud
set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=20, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

Applying NLP Methods for Text Mining and Clustering
```{r}
# Text Mining and clustering
library(tm)
library(proxy)
library(RTextTools)
library(fpc)   
library(wordcloud)
library(cluster)
library(stringi)
```
```{r}
corpus = Corpus(VectorSource(pinot$description))
# summary(corpus)

ndocs <- length(corpus)
# ignore extremely rare words i.e. terms that appear in less then 1% of the descriptions
minTermFreq <- ndocs * 0.01
# ignore overly common words i.e. terms that appear in more than 50% of the descriptions
maxTermFreq <- ndocs * .5
dtm = DocumentTermMatrix(corpus,
                         control = list(
                                        stopwords = TRUE, 
                                        wordLengths=c(4, 15),
                                        removePunctuation = T,
                                        removeNumbers = T,
                                        stemming = T,
                                        bounds = list(global = c(minTermFreq, maxTermFreq))
                                       ))
#dtm <- dtm[, names(head(sort(colSums(as.matrix(dtm))), 400))]
#dtm <- dtm[, names(sort(colSums(as.matrix(dtm))))]
#print(as.matrix(dtm))
write.csv((as.matrix(dtm)), "test.csv")
#head(sort(as.matrix(dtm)[18,], decreasing = TRUE), n=15)
dtm.matrix = as.matrix(dtm)
#wordcloud(colnames(dtm.matrix), dtm.matrix[28, ], max.words = 20)
inspect(dtm)
```
```{r}
dtm <- weightTfIdf

# dtm.matrix = as.matrix(dtm)

wordcloud(colnames(dtm.matrix), dtm.matrix[100, ], max.words = 10)
# inspect(dtm)

#write.csv((as.matrix(dtm)), "test.csv")

#head(sort(as.matrix(dtm)[1,], decreasing = TRUE), n=15)
wordcloud(colnames(dtm.matrix), dtm.matrix[12,], max.words = 10)
```


Trying to explore possible clustering using K-Means
```{r}
# Clustering - K Means - Price Vs. Points
pairs(clean_train[1:5], col = "blue", cex = 0.5, upper.panel = NULL)
df2 <- data.frame(x=clean_train$price, y=clean_train$points) 
plot(df2$x, df2$y, cex = 0.5)
#df2 <- data.frame(x=scale(clean_train$price), y=scale(clean_train$points) )
km <- kmeans(df2, centers = 5)
plot(df2$x, df2$y, cex = 0.5, col=km$cluster)
```

```{r}
# Clustering - K Means - Price Vs. Number of Words in the Description
df3 <- data.frame(x=clean_train$price, y=clean_train$desc_nw) 
plot(df2$x, df2$y, cex = 0.5)
#df2 <- data.frame(x=scale(clean_train$price), y=scale(clean_train$points) )
km <- kmeans(df3, centers = 4, nstart = 20)
plot(df3$x, df3$y, cex = 0.5, col=km$cluster, xlab="log(price)", ylab="number of words")

```

### 4. Data Encrichment - Adding Wine Chemistry Vs, Quality Dataset

Data Encrichment - Adding wine chemistry dataset
```{r}
# Enriching the data - Wine Quality according to Chemistry 

# reading the dataset
reds <- read.csv("C:/Users/Meni/Downloads/Wine_data_Red.csv")
reds$quality_as_factor <- factor(reds$quality, levels=c(0,1,2,3,4,5,6,7,8,9,10))
# reorganizing 
reds_quality_min <- min(reds$quality)
reds_quality_max <- max(reds$quality)
reds_quality_mean <- mean(reds$quality)
reds_quality_median <- median(reds$quality)
reds_quality_iqr <- IQR(reds$quality)
reds_quality_q1 <- reds_quality_median - reds_quality_iqr
reds_quality_q3 <- reds_quality_median + reds_quality_iqr

reds_quality_mode <- names(which.max(table(reds$quality)))
# cleaning outliers
reds_outliers <- sum(reds$quality < reds_quality_q1 - 1.5*reds_quality_iqr)
reds_outliers <- reds_outliers + sum(reds$quality > reds_quality_q3 + 1.5*reds_quality_iqr)

reds_quality_sd <- sd(reds$quality)

# EDA 
ggplot(data=reds, aes(x=quality)) +
    geom_bar(binwidth=1, color='black', fill='white') +
    coord_cartesian(xlim=c(0,10)) +
    geom_vline(xintercept = reds_quality_median, linetype='longdash', alpha=.5) +
    geom_vline(xintercept = reds_quality_q1 - 1.5*reds_quality_iqr, linetype='longdash', alpha=.5) +
    geom_vline(xintercept = reds_quality_q3 + 1.5*reds_quality_iqr, linetype='longdash', alpha=.5) +
    geom_vline(xintercept = reds_quality_mean, linetype=1, color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Number of Samples")
# searching for correlations
cor(x=reds[,2:12], y=reds$quality)

summary(reds$alcohol)

reds_alcohol_mean <- mean(reds$alcohol)
reds_alcohol_median <- median(reds$alcohol)

tapply(reds$alcohol, reds$quality, mean)
# plotting the alcohol percentage vs. quality
ggplot(data=reds, aes(x=quality_as_factor, y=alcohol)) +
    geom_boxplot() +
    geom_hline(show_guide=T, yintercept=reds_alcohol_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean-reds_quality_min+1, linetype='longdash', color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Alcohol")

ggplot(data=reds, aes(x=as.numeric(quality), y=alcohol)) +
    geom_jitter(alpha=1/3) +
    geom_smooth(method='lm', aes(group = 1))+
    geom_hline(yintercept=reds_alcohol_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean, linetype='longdash', color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Alcohol")

summary(reds$citric.acid)
# exploring citric acid 
reds_citric.acid_mean <- mean(reds$citric.acid)
reds_citric.acid_median <- median(reds$citric.acid)
reds_citric.acid_sd <- sd(reds$citric.acid)
reds_citric.acid_max <- max(reds$citric.acid)
caout <- (reds_citric.acid_max - reds_citric.acid_mean) / reds_citric.acid_sd

tapply(reds$citric.acid, reds$quality, mean)
# plotting the citric acid percentage vs. quality
ggplot(data=reds, aes(x=quality_as_factor, y=citric.acid)) +
    geom_boxplot() +
    geom_hline(show_guide=T, yintercept=reds_citric.acid_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean-reds_quality_min+1, linetype='longdash', color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Citric Acid")

ggplot(data=reds, aes(x=as.numeric(quality), y=citric.acid)) +
    geom_jitter(alpha=1/3) +
    geom_smooth(method='lm', aes(group = 1))+
    geom_hline(yintercept=reds_citric.acid_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean, linetype='longdash', color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Citric Acid")

summary(reds$volatile.acidity)
# exploring the volatile acidity
reds_volatile.acidity_mean <- mean(reds$volatile.acidity)
reds_volatile.acidity_median <- median(reds$volatile.acidity)
reds_volatile.acidity_sd <- sd(reds$volatile.acidity)
reds_volatile.acidity_max <- max(reds$volatile.acidity)
vaout <- (reds_volatile.acidity_max - reds_volatile.acidity_mean) / reds_volatile.acidity_sd

tapply(reds$volatile.acidity, reds$quality, mean)
# plotting the volatile acidity vs. quality
ggplot(data=reds, aes(x=quality_as_factor, y=volatile.acidity)) +
    geom_boxplot() +
    geom_hline(show_guide=T, yintercept=reds_volatile.acidity_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean-reds_quality_min+1, linetype='longdash', color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Volatile Acidity")

ggplot(data=reds, aes(x=as.numeric(quality), y=volatile.acidity)) +
    geom_jitter(alpha=1/3) +
    geom_smooth(method='lm', aes(group = 1))+
    geom_hline(yintercept=reds_volatile.acidity_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean, linetype='longdash', color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("Volatile Acidity")

reds <- transform(reds, is.faulty = quality<5)
# defining wines which are considered low level, or faulty
faulty.reds <- table(reds$is.faulty)

ggplot(data=reds, aes(x=is.faulty, y=volatile.acidity)) +
    geom_boxplot() +
    geom_hline(show_guide=T, yintercept=reds_volatile.acidity_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean-reds_quality_min+1, linetype='longdash', color='blue', alpha=.5) +
    xlab("Faulty Wine") +
    ylab("Volatile Acidity")

summary(subset(reds, is.faulty)$volatile.acidity)
# plotting faluty wines vs. alcohol percentage
ggplot(data=reds, aes(x=is.faulty, y=alcohol)) +
    geom_boxplot() +
    geom_hline(show_guide=T, yintercept=reds_alcohol_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean-reds_quality_min+1, linetype='longdash', color='blue', alpha=.5) +
    xlab("Faulty Wine") +
    ylab("Alcohol")

summary(subset(reds, is.faulty)$alcohol)
# plotting faluty wines vs. citric acid
ggplot(data=reds, aes(x=is.faulty, y=citric.acid)) +
    geom_boxplot() +
    geom_hline(show_guide=T, yintercept=reds_citric.acid_mean, linetype='longdash', alpha=.5, color='blue') +
    geom_vline(xintercept = reds_quality_mean-reds_quality_min+1, linetype='longdash', color='blue', alpha=.5) +
    xlab("Faulty Wine") +
    ylab("Citric Acid")

summary(subset(reds, is.faulty)$citric.acid)

cor(x=reds$volatile.acidity, y=reds$citric.acid)

library(ggplot2)
ggplot(data=reds, aes(x=quality)) +
    geom_bar(binwidth=1, color='black', fill='white') +
    coord_cartesian(xlim=c(0,10)) +
    geom_vline(xintercept = reds_quality_median, linetype='longdash', alpha=.5) +
    geom_vline(xintercept = reds_quality_q1 - 1.5*reds_quality_iqr, linetype='longdash', alpha=.5) +
    geom_vline(xintercept = reds_quality_q3 + 1.5*reds_quality_iqr, linetype='longdash', alpha=.5) +
    geom_vline(xintercept = reds_quality_mean, linetype=1, color='blue', alpha=.5) +
    xlab("Wine Quality") +
    ylab("# Samples")

reds$quality.cut <- cut(reds$quality, breaks=c(0,4,6,10))
ggplot(data=reds, aes(x=alcohol, y=citric.acid)) +
    coord_cartesian(
        xlim=c(quantile(reds$alcohol,.01),quantile(reds$alcohol,.99)),
        ylim=c(quantile(reds$citric.acid,.01),quantile(reds$citric.acid,.99))
        ) +
    geom_jitter(alpha=.5, aes(size=quality.cut, color=quality.cut)) +
    geom_vline(xintercept = reds_alcohol_mean, linetype='longdash', color='blue', alpha=.5) +
    geom_hline(yintercept = reds_citric.acid_mean, linetype='longdash', color='blue', alpha=.5) +
    xlab("Alcohol") +
    ylab("Citric Acid")

reds <- transform(
        reds,
        quadrant = ifelse(alcohol>reds_alcohol_mean,
                          ifelse(citric.acid>reds_citric.acid_mean,4,2),
                          ifelse(citric.acid>reds_citric.acid_mean,3,1))
    )

table(reds$quadrant)

sort(tapply(reds$is.faulty, reds$quadrant, mean))

sort(tapply(reds$volatile.acidity>reds_volatile.acidity_mean, reds$quadrant, mean))

cor(x=reds$volatile.acidity, y=reds$citric.acid)



```


