```{r}
library(sqldf)
library(plotly)
#install.packages("leaflet")
#install.packages("leaflet.extras")
library(leaflet)
library(leaflet.extras)
library(ggplot2)
library(wordcloud2)
library(tm)
library(ggmap)
library(dbscan)
```


---
title: "Hotels_Review_Clustering"
author: "Noa"
date: "February 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Booking.com Hotels Review Clustering Presentation

The data is a Kaggle dataset including information of close to 0.5M Hotel reviews in Europe
https://www.kaggle.com/jiashenliu/515k-hotel-reviews-data-in-europe

We will base our models and analysis on the earlier EDA and Regression work done.

Lets start by uploading aggregated hotels data and visitors (based on the reviews)


```{r }
rm(list=ls())
setwd("C:/Users/noaba/Documents/Private/IDC_MBA/R/Clustering")
list.files()
df.hotel <-read.csv("Hotels_Review_Aggregated_2.csv")
names(df.hotel)
```

#Starting with some additional Exploratory

We will see the affect of complains about the breakfast to the avg hotel score

```{r }
ggplot(df.hotel, aes(x=df.hotel$Complains_Breakfast, y=df.hotel$Average_Score)) + geom_point() +geom_smooth(method=lm, color="red") + theme_linedraw() + xlab("% Complains on Breakfast") + ylab("Avg. Score")
```
We will see the affect of complains about the breakfast to the avg hotel score

```{r}
ggplot(df.hotel, aes(x=df.hotel$Complains_Price, y=df.hotel$Average_Score)) + geom_point() +geom_smooth(method=lm, color="green")+ theme_linedraw() + xlab("% Complains on Price") + ylab("Avg. Score")


ggplot(df.hotel, aes(x=(1-df.hotel$resident_stays), y=df.hotel$Avg_Stay_Duration)) + geom_point() +geom_smooth(method=lm, color="purple")+ theme_bw() + xlab("% Non Resident Stays") + ylab("Avg. Stay Duration")

ggplot(df.hotel, aes(x=df.hotel$business_trips, y=df.hotel$Complains_Wifi)) + geom_point() +geom_smooth(method=lm, color="yellow")+ theme_bw() + xlab("% Business Trips") + ylab("% complains on Wifi")
```

Lets look at the distrobution of hotels over map

```{r}
leaflet(data = df.hotel)%>%addProviderTiles(providers$Stamen.TonerLite)%>%addMarkers(popup = ~df.hotel$Name,clusterOptions = markerClusterOptions())%>%addTiles()
```


# Filtering to London, UK hotels only

Creating a subset of hotels for London UK only for the clustering practice
To avoid local colture to skew results

```{r}
df.hotel.uk <- df.hotel[which(grepl("United Kingdom",df.hotel$Country)),]
leaflet(data = df.hotel.uk)%>%addProviderTiles(providers$Stamen.TonerLite)%>%addMarkers(popup = ~df.hotel.uk$Name,clusterOptions = markerClusterOptions())%>%addTiles()
```

```{r}
pairs(df.hotel.uk[6:25], col = "magenta", cex = 0.2, upper.panel = NULL)
cor(df.hotel.uk[6:25],df.hotel.uk[6:25])
```

## Clustering Hotels By Location (Lat-Lan)

We will examine two options for clustering using both DBSCAN and K-Means

# Clustering Hotels by Location using K-Means
```{r}
set.seed(1)
lat <- df.hotel.uk$lat
lng <-df.hotel.uk$lng
kmloc <- kmeans(cbind(lat, lng), centers = 8)
plot(lng, lat, col = kmloc$cluster, pch = 20)
```

```{r}
df.hotel.uk.kmloc <- df.hotel.uk
df.hotel.uk.kmloc$km <-kmloc$cluster
# Create a palette that maps factor levels to colors
pal <- colorFactor(c("red","green","yellow","magenta", "orange", "blue","black","turquoise"), domain = c(1,2,3,4,5,6,7,8))

leaflet(df.hotel.uk.kmloc) %>% addTiles() %>%
  addCircleMarkers(
    radius = 4,
    color = ~pal(df.hotel.uk.kmloc$km),
    stroke = FALSE, fillOpacity = 0.9,  popup = ~df.hotel.uk.kmloc$Name
  ) %>% addProviderTiles(providers$Stamen.TonerLite) 


```

# Clustering Hotels by Location using DBSCAN
```{r}
dbsloc <- dbscan(cbind(lat, lng), MinPts = 200, eps = 0.05)
dbsloc
dbsloc
plot(lng, lat, cex = 1,col=dbsloc$cluster+1,pch=16)
```

```{r}
df.hotel.uk.dbloc <- df.hotel.uk
df.hotel.uk.dbloc$km <-dbsloc$cluster
# Create a palette that maps factor levels to colors
pal <- colorFactor(c("red","blue","black"), domain = c(0,1,2))

leaflet(df.hotel.uk.dbloc) %>% addTiles() %>%
  addCircleMarkers(
    radius = 3,
    color = ~pal(df.hotel.uk.dbloc$km),
    stroke = FALSE, fillOpacity = 0.9,  popup = ~df.hotel.uk.dbloc$km
  ) %>% addProviderTiles(providers$Stamen.TonerLite) 

```

## PCA - Dimentionality Reduction


``` {r}
set.seed(1)
pc = prcomp(df.hotel.uk[,9:15], center = TRUE, scale. = TRUE)
pc
```

Visualizing the components

``` {r}
pc.var =pc$sdev ^2
pc.per = pc.var/sum(pc.var)
plot(pc.per)
biplot(pc, cex=0.5)
```

## Personalizing Hotels by Traveler Type - Clustering

```{r}
set.seed(2)

km.travel <- kmeans(df.hotel.uk[,c(9:14)], centers=3)

df.hotel.uk.km <- df.hotel.uk
df.hotel.uk.km$km <-km.travel$cluster

km.travel$centers

```

```{r}
# Create a palette that maps factor levels to colors
pal <- colorFactor(c("magenta", "black", "blue"), domain = c(1, 2, 3))

leaflet(df.hotel.uk.km) %>% addTiles() %>%
  addCircleMarkers(
    radius = 5,
    color = ~pal(df.hotel.uk.km$km),
    stroke = FALSE, fillOpacity = 0.8,  popup = ~df.hotel.uk.km$Name
  ) %>% addProviderTiles(providers$CartoDB.Positron) 

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
