---
output:
  pdf_document: default
  html_document: default
---
```{r}
library(ggmap)
library("dplyr")
library(sqldf)
library(ggplot2)
library(reshape)
library(wordcloud2)
library(tm)
install.packages("")

```


---
title: "Hotels_Review_EDA_and_Regression"
author: "Yanir, Kobi & Noa"
date: "December 18, 2017"
output: html_document
---

## Reading and Understanding Hotel Reviews Data

The data is a Kaggle dataset including information of close to 0.5M Hotel reviews in Europe
https://www.kaggle.com/jiashenliu/515k-hotel-reviews-data-in-europe

Reading the raw data from Kaggle to df.raw

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Change this path to download files going forward
setwd("C:/Users/noaba/Documents/Private/IDC_MBA/R/Regression")

df.raw <- read.csv("hotel_reviews.csv")

```

## Kaggle Raw Data Cleansing and Transformation

Signals for reviewer including:
1. Is submitted from Mobile - 0/1
2. Is Business trip - 0/1
3. Is the traveler traveling in Couple - 0/1
4. Is the traveler traveling with Pet - 0/1
5. Is the traveler Family with young children - 0/1
6. Is the traveler Family with older children - 0/1
7. Is the traveling Solo traveler - 0/1
8. Is the Traveler Group - 0/1
9. Stay duration by number of days, if missing apply mean value
10. Hotel Country - extract from hotel address
11. Calculate if the reviewer is resident of the hotel - 0/1
11. Signals for strong positive and negative words (if exist in review)
  11.i Positive: "Clean", "Location"
  11.ii Negative: "Breakfast", "Expensive"
12. Negative word precentage calculation from total words in review
13. Calculate if the review is strongly positive - 1/0

```{r}
df.raw$submitted_from_mobile = ifelse(grepl("mobile",df.raw$Tags),1,0)
df.raw$is_business_travel = ifelse(grepl("Business trip",df.raw$Tags),1,0)
df.raw$is_couple = ifelse(grepl("Couple",df.raw$Tags),1,0)
df.raw$with_pet = ifelse(grepl("With a pet",df.raw$Tags),1,0)
df.raw$Family_young_children = ifelse(grepl("Family with young children",df.raw$Tags),1,0)
df.raw$Familty_older_children = ifelse(grepl("Family with older children",df.raw$Tags),1,0)
df.raw$solo_traveler = ifelse(grepl("Solo",df.raw$Tags),1,0)
df.raw$group = ifelse(grepl("Group",df.raw$Tags),1,0)

# Add stay duration based on tags
df.raw$stay_duration = c(rep(0,length(df.raw$Hotel_Name)))
df.raw$stay_duration[which(grepl("Stayed 1 night",df.raw$Tags))] <- 1
df.raw$stay_duration[which(grepl("Stayed 2 nights",df.raw$Tags))] <- 2
df.raw$stay_duration[which(grepl("Stayed 3 nights",df.raw$Tags))] <- 3
df.raw$stay_duration[which(grepl("Stayed 4 nights",df.raw$Tags))] <- 4
df.raw$stay_duration[which(grepl("Stayed 5 nights",df.raw$Tags))] <- 5
df.raw$stay_duration[which(grepl("Stayed 6 nights",df.raw$Tags))] <- 6
df.raw$stay_duration[which(grepl("Stayed 7 nights",df.raw$Tags))] <- 7
df.raw$stay_duration[which(grepl("Stayed 8 nights",df.raw$Tags))] <- 8
df.raw$stay_duration[which(grepl("Stayed 9 nights",df.raw$Tags))] <- 9
df.raw$stay_duration[which(grepl("Stayed 10 nights",df.raw$Tags))] <- 10
df.raw$stay_duration[which(grepl("Stayed 11 nights",df.raw$Tags))] <- 11
df.raw$stay_duration[which(grepl("Stayed 12 nights",df.raw$Tags))] <- 12
df.raw$stay_duration[which(grepl("Stayed 13 nights",df.raw$Tags))] <- 13
df.raw$stay_duration[which(grepl("Stayed 14 nights",df.raw$Tags))] <- 14
df.raw$stay_duration[which(grepl("Stayed 15 nights",df.raw$Tags))] <- 15
df.raw$stay_duration[which(grepl("Stayed 16 nights",df.raw$Tags))] <- 16
df.raw$stay_duration[which(grepl("Stayed 17 nights",df.raw$Tags))] <- 17
df.raw$stay_duration[which(grepl("Stayed 18 nights",df.raw$Tags))] <- 18
df.raw$stay_duration[which(grepl("Stayed 19 nights",df.raw$Tags))] <- 19
df.raw$stay_duration[which(grepl("Stayed 20 nights",df.raw$Tags))] <- 20
df.raw$stay_duration[which(grepl("Stayed 21 nights",df.raw$Tags))] <- 21
df.raw$stay_duration[which(grepl("Stayed 22 nights",df.raw$Tags))] <- 22
df.raw$stay_duration[which(grepl("Stayed 23 nights",df.raw$Tags))] <- 23
df.raw$stay_duration[which(grepl("Stayed 24 nights",df.raw$Tags))] <- 24
df.raw$stay_duration[which(grepl("Stayed 25 nights",df.raw$Tags))] <- 25
df.raw$stay_duration[which(grepl("Stayed 26 nights",df.raw$Tags))] <- 26
df.raw$stay_duration[which(grepl("Stayed 27 nights",df.raw$Tags))] <- 27
df.raw$stay_duration[which(grepl("Stayed 28 nights",df.raw$Tags))] <- 28
df.raw$stay_duration[which(grepl("Stayed 29 nights",df.raw$Tags))] <- 29
df.raw$stay_duration[which(grepl("Stayed 30 nights",df.raw$Tags))] <- 30
df.raw$stay_duration[which(grepl("Stayed 31 nights",df.raw$Tags))] <- 31

#applying avg nights stays where the value is missing
df.raw$stay_duration[which(df.raw$stay_duration == 0)] <- round(mean(df.raw$stay_duration))

# Setting the hotel Country from Address - to find later if stays were resident and different messurements for predictions
df.raw$Hotel_country = c(rep("", length(df.raw$Hotel_Name)))
df.raw$Hotel_country[which(grepl("United Kingdom",df.raw$Hotel_Address))] <- " United Kingdom "
df.raw$Hotel_country[which(grepl("France",df.raw$Hotel_Address))] <- " France "
df.raw$Hotel_country[which(grepl("Austria",df.raw$Hotel_Address))] <- " Austria "
df.raw$Hotel_country[which(grepl("Spain",df.raw$Hotel_Address))] <- " Spain "
df.raw$Hotel_country[which(grepl("Netherland",df.raw$Hotel_Address))] <- " Netherland "
df.raw$Hotel_country[which(grepl("Italy",df.raw$Hotel_Address))] <- " Italy "
                         
df.raw$Reviewer_Nationality <- as.character(df.raw$Reviewer_Nationality)

# Will set resident signal 1 when the nationality of reviewer similar to the Hotel Country
df.raw$is_resident = c(rep(0,length(df.raw$Hotel_Name)))
df.raw$is_resident[which(df.raw$Hotel_country == df.raw$Reviewer_Nationality)] <- 1

df.raw$Negative_Review <- tolower(df.raw$Negative_Review)
df.raw$Positive_Review <- tolower(df.raw$Positive_Review)

# Picking on strong features from the data 
df.raw$Complain_Breakfast <- ifelse(grepl("breakfast",df.raw$Negative_Review),1,0)
df.raw$Complain_Price <- ifelse(grepl("expensive",df.raw$Negative_Review) | grepl("price",df.raw$Negative_Review) | grepl("charge",df.raw$Negative_Review),1,0)
df.raw$Complain_Wifi <- ifelse(grepl("wifi",df.raw$Negative_Review) | grepl("wi fi",df.raw$Negative_Review) | grepl("internet",df.raw$Negative_Review),1,0)

df.raw$Positive_Clean <- ifelse(grepl("clean",df.raw$Positive_Review),1,0)
df.raw$Positive_Breakfast <- ifelse(grepl("breakfast",df.raw$Positive_Review),1,0)

# Calculate negative words precentage from overall number of words in review
df.raw$Negative_Words_pct <- df.raw$Review_Total_Negative_Word_Counts/(df.raw$Review_Total_Negative_Word_Counts+df.raw$Review_Total_Positive_Word_Counts)
# Correct values where positive review is missing (to avoide NA)
df.raw$Negative_Words_pct[which(is.na(df.raw$Negative_Words_pct))] <- ifelse(df.raw$Review_Total_Negative_Word_Counts[which(is.na(df.raw$Negative_Words_pct))]>2,1,0)


# Calculate if the review is strongly positive
df.raw$is_positive <- df.raw$Reviewer_Score > 8.5

df.raw$Review_Date <- as.Date(as.character(df.raw$Review_Date),"%m/%d/%Y")

df.raw$day_of_the_week <- weekdays(as.Date(df.raw$Review_Date))


```


The data presented is a multi_dimentional combination of data gatherd from Booking.com (through Kaggle), different location based 
information (gathered through Google Maps APIs and Yelp APIs), with the help of extrapulation methods from Review Tags

```{r show raw dataframe}
str(df.raw)
```

Will check if there are any missing values that might interefere us, clean up of data
```{r}
colSums(is.na(df.raw))

#we will remove the entries which has NA in Lat/Lng
df.raw <- df.raw[-which(is.na(df.raw$lat)),] 

df.raw$Hotel_Name <- as.character(df.raw$Hotel_Name)

# There are few hotels sharing the same name - will drop them to avoid confusion
df.raw <- df.raw[-which(df.raw$Hotel_Name == "Hotel Regina"),] 

```

## Hotels Dataset & Aggregations

Generating Hotels data set including specific Hotels data (unique lists of hotels charactaristics and aggregations). 
Signals , aggregation including:
1-6. Original Hotel Name, Country, lat/lng, Avrage Score
7. Total Reviews recorded in Kaggle dataset (for the further precentage and measurements)
8. Total stay duration in the hotel
9. Precentage of Hotel Business travelers from reviews
10. Precentage of Hotel Couple travelers from reviews
11. Precentage of Hotel travelers with pets from reviews
12. Precentage of Hotel Family with young children from reviews
13. Precentage of Hotel Family with older children from reviews
14. Precentage of Hotel Solo travelers from reviews
15. Precentage of Hotel country resident travelers from reviews
16. Overall positive word count - negative word cound from the hotel review texts
17. Precentage signals for strong positive and negative words (if exist in review)
  17-18.i Positive: "Clean", "Breakfast"
  19-21.ii Negative: "Breakfast", ("Expensive" or "Price" or "Charge"), ("Wifi" or "wi fi" or "internet")
22. Avg. stay duration in the hotel


```{r}
df.hotels <- data.frame(df.raw$Hotel_Name, df.raw$Hotel_country, df.raw$Hotel_Address, df.raw$lat, df.raw$lng, df.raw$Average_Score)

colnames(df.hotels) = c('Name','Country','Address', 'lat','lng', 'Average_Score')

df.hotels <- unique(df.hotels)

# 7 Calculate Real number of reviews we have in the data set
agg_stay <- aggregate(df.raw$is_resident ~ df.raw$Hotel_Name, data = df.raw, length)
colnames(agg_stay) = c('Name','Num_of_Reviews')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

# 8 Total duration stayed at the hotel
agg_stay <- aggregate(df.raw$stay_duration ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','total_stay_duration')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

# 9 Total Business + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$is_business_travel ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','business_trips')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$business_trips <- df.hotels$business_trips/df.hotels$Num_of_Reviews

# 10 Total couple stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$is_couple ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','couples_stay')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$couples_stay <- df.hotels$couples_stay/df.hotels$Num_of_Reviews

# 11 Total pet stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$with_pet ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','pet_stay')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$pet_stay <- df.hotels$pet_stay/df.hotels$Num_of_Reviews

# 12 Total Family with older Children stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Familty_older_children ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','family_with_older_stays')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$family_with_older_stays <- df.hotels$family_with_older_stays/df.hotels$Num_of_Reviews

# 13 Total Family with young Children stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Family_young_children ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','family_with_younger_stays')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$family_with_younger_stays <- df.hotels$family_with_younger_stays/df.hotels$Num_of_Reviews

# 14 Total Solo Traveler stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$solo_traveler ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','solo_stays')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$solo_stays <- df.hotels$solo_stays/df.hotels$Num_of_Reviews

# 15 Total Group Travel stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$group ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','group_stays')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$group_stays <- df.hotels$group_stays/df.hotels$Num_of_Reviews

# 16 Total resident Travel stays + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$is_resident ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','resident_stays')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$resident_stays <- df.hotels$resident_stays/df.hotels$Num_of_Reviews

# 17 Total Positive - Negative word count
agg_stay <- aggregate((df.raw$Review_Total_Positive_Word_Counts - df.raw$Review_Total_Negative_Word_Counts) ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','positive_minus_negative_word_count')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')


# 18 Total #reviews complaining on the breakfast  + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Complain_Breakfast ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','Complains_Breakfast')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$Complains_Breakfast <- df.hotels$Complains_Breakfast/df.hotels$Num_of_Reviews

# 19 Total #reviews complaining on the price  + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Complain_Price ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','Complains_Price')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$Complains_Price <- df.hotels$Complains_Price/df.hotels$Num_of_Reviews

# 20 Total #reviews complaining on the wifi  + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Complain_Wifi ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','Complains_Wifi')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$Complains_Wifi <- df.hotels$Complains_Wifi/df.hotels$Num_of_Reviews


# 21 Total #positive reviews mentioning room is clean  + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Positive_Clean ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','Positives_Clean')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$Positives_Clean <- df.hotels$Positives_Clean/df.hotels$Num_of_Reviews

# 22 Total #positive reviews mentioning location  + calculation fo precentage of stays
agg_stay <- aggregate(df.raw$Positive_Breakfast ~ df.raw$Hotel_Name, data = df.raw, sum)
colnames(agg_stay) = c('Name','Positives_Breakfast')
df.hotels <- merge(df.hotels,agg_stay, by ='Name')

df.hotels$Positives_Breakfast <- df.hotels$Positives_Breakfast/df.hotels$Num_of_Reviews

df.hotels$Avg_Stay_Duration <- df.hotels$total_stay_duration / df.hotels$Num_of_Reviews

summary(df.hotels)
```

Merging to the Hotels table different set of data we aquired from Yelp, to indicate number of businesses in 100M, 1KM & 5KM

```{r}

df.enrich.raw <- read.csv("hotel_reviews_enriched.csv")

#we will remove the entries which has NA in Lat/Lng
df.enrich.raw <- df.enrich.raw[-which(is.na(df.enrich.raw$Hotel_lat)),] 

df.enrich.raw$Hotel_Name <- as.character(df.enrich.raw$Hotel_Name)

# There are few hotels sharing the same name - will drop them to avoid confusion
df.enrich.raw <- df.enrich.raw[-which(df.enrich.raw$Hotel_Name == "Hotel Regina"),] 


df.yelp <- data.frame(df.enrich.raw$Hotel_Name, df.enrich.raw$Businesses_100m,df.enrich.raw$Businesses_1km, df.enrich.raw$Businesses_5km)

df.yelp <- unique(df.yelp)

colnames(df.yelp) = c('Name','Businesses_100m','Businesses_1km','Businesses_5km')

df.hotels <- merge(df.hotels,df.yelp, by ='Name')


#Write back the aggregated data collected and calculated
write.csv(df.hotels, file="Hotels_Review_Aggregated_2.csv", quote=FALSE, na="NA", row.names=FALSE)
write.csv(df.raw, file = "Hotels_Review_Numeric_2.csv", na="NA", row.names=FALSE)


```



## Ploting the Data
Calculating and goruping avrage hotel rating by country
```{r}

df.hotels %>% 
  select(Average_Score, Country) %>% 
  group_by(Country) %>%   
  summarise(trav_type_avg = mean(Average_Score)) %>% 
  ggplot(aes(x = reorder(Country, -trav_type_avg), trav_type_avg , fill = Country)) +
  geom_bar(stat = "identity") +
  ggtitle("Average rating by Country") +
  xlab("Country") + ylab("Average rating") +scale_fill_grey(start = 0.1, end = 0.6, na.value = "red")
  

# Can also check which country is more mobile oriented (reviewer nationality, is mobile)
```
Plotting the precentage of stays by travel types by country

```{r}

  df.hotels_full <- df.hotels

for (i in 8:15) {
  df.hotels_full[,i] <- df.hotels_full[,i]* df.hotels_full[,6]
}
  
w2l <- function(df.hotels_full) melt(df.hotels_full, measure.vars = colnames(df.hotels_full)[8:15])
mdfr_linear <- w2l(df.hotels_full)

ggplot(mdfr_linear, aes(x= mdfr_linear$Country, y = mdfr_linear$value, fill = variable)) +
geom_bar(position = "stack", stat = "identity") +
   coord_flip() + xlab("") + ylab("Number of Reviews") +
    scale_fill_brewer(type = "div") + theme(legend.position = "top")

```

Plotting the avg. review score , grouped by the different traveler type to visualize the type of travelers most positive and negative trends


```{r}
travel_avg_score <- data.frame(c("Couple", "Group", "Solo Traveler", "With Pet", "Family with older children", "Family with young children"))

colnames(travel_avg_score) = c('Traveler_Type')

travel_avg_score$Avg_Review_Score = c(mean(df.raw$Reviewer_Score[which(df.raw$is_couple == 1)]), +
                                        mean(df.raw$Reviewer_Score[which(df.raw$group == 1)]), +
                                        mean(df.raw$Reviewer_Score[which(df.raw$solo_traveler == 1)]), +
                                        mean(df.raw$Reviewer_Score[which(df.raw$with_pet == 1)]), +
                                        mean(df.raw$Reviewer_Score[which(df.raw$Familty_older_children == 1)]), mean(df.raw$Reviewer_Score[which(df.raw$Family_young_children == 1)]))

  ggplot(travel_avg_score, aes(x= reorder(Traveler_Type,Avg_Review_Score), y = Avg_Review_Score, fill = Traveler_Type)) +
   geom_bar(position = "stack", stat = "identity") +
   coord_flip() +
   xlab("") +
   ylab("Avg. Review Score") +
    scale_fill_brewer(type = "div") 



```

Plotting the number of reviews by the day of the week, as well as the avg. score by the day of the week

```{r}
#day_of_the_week = c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday","Friday", "Saturday")
day_of_the_week = format.factor(c(1,2,3,4,5,6,7))

df_day_score <- data.frame(factor(day_of_the_week, levels = day_of_the_week))
df_day_score$Avg_Score <- c(mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 1)]),
                            mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 2)]),
                            mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 3)]),
                            mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 4)]),
                            mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 5)]),
                            mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 6)]),
                            mean(df.enrich.raw$Reviewer_Score[which(df.enrich.raw$Day_of_Week == 7)]))

df_day_score$Avg_Score = format(round(df_day_score$Avg_Score, 2), nsmall = 2)

df_day_score$number_of_reviews <- c(length(which(df.enrich.raw$Day_of_Week == 1)),
                                    length(which(df.enrich.raw$Day_of_Week == 2)),
                                    length(which(df.enrich.raw$Day_of_Week == 3)),
                                    length(which(df.enrich.raw$Day_of_Week == 4)),
                                    length(which(df.enrich.raw$Day_of_Week == 5)),
                                    length(which(df.enrich.raw$Day_of_Week == 6)),
                                    length(which(df.enrich.raw$Day_of_Week == 7)))

#$name <- factor(x$name, levels = x$name[order(x$val)])
#x$name

  ggplot(df_day_score, aes(x= day_of_the_week, y = number_of_reviews, fill = day_of_the_week)) +
   geom_bar(position = "stack", colour="black", stat = "identity") +
   xlab("") +
   ylab("Number of Reviews") +
    scale_fill_brewer(type = "div", palette = "Browns") +
        theme(legend.position = "bottom") + theme_bw()  + geom_label(aes(label=Avg_Score),fill = ifelse(df_day_score$Avg_Score>8.47,"light green","dark grey"), hjust=0.5, vjust=-0.5, colour = "black", fontface = "bold")
```



```{r}
  ggplot(df_day_score, aes(x= reorder(day_of_the_week, Avg_Score), y = Avg_Score, fill = day_of_the_week)) +
   geom_bar(position = "stack", stat = "identity") +
       coord_flip() +
   xlab("") +
   ylab("Avg. Review Score") +
    scale_fill_brewer(type = "div", palette = "Purples")+
    theme(legend.position = "bottom")
  

```

Showing trend of reviews by Mobile and PC over time - 
Aggregating the data by months, and visualizing over graph chart

```{r}
mo_yr <- format(df.raw$Review_Date,"1-%B-%Y")
mo_yr <- as.Date(as.character(mo_yr),"%d-%B-%Y")

Mobile_vs_PC.agg <- aggregate(df.raw$submitted_from_mobile ~ mo_yr, df.raw, FUN = sum)
PC_vs_Mobile.agg <- aggregate(1-df.raw$submitted_from_mobile ~ mo_yr, df.raw, FUN = sum)

colnames(Mobile_vs_PC.agg) = c('Date','Reviews_through_mobile')
colnames(PC_vs_Mobile.agg) = c('Date','Reviews_through_PC')

Mobile_vs_PC.agg <- merge(Mobile_vs_PC.agg,PC_vs_Mobile.agg, by ='Date')[1:24,]

meltf2 <- function(Mobile_vs_PC.agg) melt(Mobile_vs_PC.agg, measure.vars = colnames(Mobile_vs_PC.agg)[2:3])
PC_vs_Mobile.agg <- meltf2(Mobile_vs_PC.agg)

ggplot(PC_vs_Mobile.agg, aes(x=PC_vs_Mobile.agg$Date, y=value))+
geom_line() + geom_point() + aes(color=variable) + xlab("Date") + ylab("Num. of Reviews") + theme(legend.position = "bottom") +  theme_bw()
```

We will try to understand if there is any relationship from media (Mobile / non-Mobile) to number of words in review.

1. Relationship between total words used (Positive + Negative) to the media used (Mobile / PC)

```{r}
ggplot(df.raw, aes(x=(df.raw$Review_Total_Negative_Word_Counts+df.raw$Review_Total_Positive_Word_Counts),y=df.raw$submitted_from_mobile))+ geom_point(size=0.3) + aes(color=df.raw$submitted_from_mobile) + geom_jitter() + ggtitle("Comperison of Total Words Used for Reviews in Mobile vs. PC")

ggplot(df.raw, aes(x=(df.raw$Review_Total_Negative_Word_Counts+df.raw$Review_Total_Positive_Word_Counts),y=df.raw$submitted_from_mobile))+ geom_point(size=0.3) + aes(color=factor(df.raw$submitted_from_mobile) + geom_jitter() + ggtitle("Comperison of Total Words Used for Reviews in Mobile vs. PC")

```

2. Relationship between Positive word counts used to the media used (Mobile / PC)

```{r}
# Reviewers might use the same ammount of words describing negative reviews from mobile, however will use less words for positive reviews
ggplot(df.raw, aes(x=(df.raw$Review_Total_Positive_Word_Counts),y=df.raw$submitted_from_mobile))+ geom_point(size=0.2) + aes(color=df.raw$submitted_from_mobile) + geom_jitter() + xlab("Total Positive Words in Review") + ylab("Submitted through PC; Submitted through Mobile") + ggtitle("Comperison of Total Positive Words Used for Reviews in Mobile vs. PC")
```

## Test Mining and Word Cloud

Find strong words repeating in positive and negative review and compare between business traverelers reviews and general (sample) population reviews

```{r}

BusinessReviews <- df.raw[sample(nrow(df.raw[which(df.raw$is_business_travel==1),]), 40000), ]
BusinessReviews <- BusinessReviews[BusinessReviews$Review_Total_Negative_Word_Counts > 2, ]
BusinessReviews <- BusinessReviews[BusinessReviews$Review_Total_Positive_Word_Counts > 2, ]

reviews <- df.raw[sample(nrow(df.raw), 40000), ]
reviews <- reviews[reviews$Review_Total_Negative_Word_Counts > 2, ]
reviews <- reviews[reviews$Review_Total_Positive_Word_Counts > 2, ]
term_freq <- function(df,sent){
  if(sent=='pos'){
       corpus <- Corpus(VectorSource(df$Positive_Review))
  }else{
       corpus <- Corpus(VectorSource(df$Negative_Review))
  }
  corpus <- tm_map(corpus, removeWords, stopwords("SMART"))
  corpus <- tm_map(corpus, removeWords, stopwords("en"))
  corpus <- tm_map(corpus, stripWhitespace)
  corpus <- tm_map(corpus, removeWords, "The")
  dtm <-TermDocumentMatrix(corpus)
  mat_dtm <- as.matrix(dtm)
  v_dtm <- sort(rowSums(mat_dtm),decreasing = TRUE)
  FreqMat <- data.frame(word = names(v_dtm), Freq = v_dtm)
  FreqMat <- FreqMat[1:50,]
  return(FreqMat)
}

GenFreqPos <- term_freq(reviews,'pos')
BusFreqPos <- term_freq(BusinessReviews,'pos')
GenFreqNeg <- term_freq(reviews,'neg')
BusFreqNeg <- term_freq(BusinessReviews,'neg')

wordcloud2(data = term_freq(reviews,'pos'),minRotation = 0,maxRotation = 0)
```



```{r}
wordcloud2(data = term_freq(reviews,'neg'),minRotation = 0,maxRotation = 0)
```

```{r}
reviews <- df.raw[sample(nrow(df.raw), 40000), ]
reviews <- reviews[reviews$Review_Total_Negative_Word_Counts > 2, ]
reviews <- reviews[reviews$Review_Total_Positive_Word_Counts > 2, ]
wordcloud2(data = term_freq(reviews,'neg'),minRotation = 0,maxRotation = 0)
```

We will use later the comparison between GenFreqNeg list to BusFreqNeg
As well as GenFreqPos list to the BusFrenPos list to identify stronger features fro business travels


```{r}

df.hotels$Businesses_100m <- as.numeric(df.hotels$Businesses_100m)
df.hotels$Businesses_1km <- as.numeric(df.hotels$Businesses_1km)
df.hotels$Businesses_5km <- as.numeric(df.hotels$Businesses_5km)

hist(df.raw$Reviewer_Score, main = "Review Score Distribution", xlab = "Score 1-10", ylab = "Number of Reviews", border = "darkgreen", col = "lightblue", xlim = c(2,10), breaks = 50)

hist(df.hotels$Average_Score, main = "Hotels Avg. Review Score Distribution", xlab = "Score 1-10", ylab = "Number of Hotels", border = "gold", col = "magenta", xlim = c(2,10), breaks = 50)

df.br <- df.raw[which(df.enrich.raw$Hotel_Name == "Britannia International Hotel Canary Wharf"),] 
ggplot(df.br, aes(x=df.br$Review_Total_Negative_Word_Counts, y=df.br$Reviewer_Score)) + geom_point() + geom_jitter() 



```



```{r}




``